
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "readme"
%%% End: 


\section{Supported Games}

At the moment the following games have been reported to work, and should
be playable to the end. However, this list generally applies to PC versions.
Mac versions should work after being ``ReSCUMM'ed'' (see later in this document),
and Amiga versions of games may work with the 'Amiga' flag turned on -- but
this is not always true.

\begin{itemize}
\item SCUMM Games:\\
  \begin {tabular} [h] {ll}
    Maniac Mansion (Classic Version)&                [Game: maniac]\\
    Maniac Mansion (Enhanced Version)&               [Game: maniac]\\
    Zak McKracken (Classic Version)&                 [Game: zak]\\
    Zak McKracken (Enhanced Version)&                [Game: zak]\\
    Indiana Jones \& the Last Crusade (EGA)&          [Game: indy3ega]\\
    Indiana Jones \& the Last Crusade (256)&          [Game: indy3]\\
    Indiana Jones \& the Last Crusade (256 FM Towns)& [Game: indy3towns]\\
    Loom (16 color floppy version)&                  [Game: loom]\\
    Loom (256 FM Towns)&                             [Game: loomtowns]\\
    Loom (256 color CD version)&                     [Game: loomcd]\\
    Zak McKracken (256 FM Towns)&                    [Game: zaktowns]\\
    Monkey Island 1 (EGA)&                           [Game: monkeyega]\\
    Monkey Island 1 (VGA)&                           [Game: monkeyvga]\\
    Monkey Island 1 (CD)&                            [Game: monkey/monkey1]\\
    Monkey Island 2&                                 [Game: monkey2]\\
    Indiana Jones and the Fate of Atlantis&          [Game: atlantis]\\
    Day of the Tentacle&                             [Game: tentacle]\\
    Sam \& Max&                                       [Game: samnmax]\\
    The Dig&                                        [Game: dig]\\
    Curse of Monkey Island&                          [Game: comi]\\
    Full Throttle&                                 [Game: ft]\\
  \end{tabular}
\item Other Games:\\ 
  \begin{tabular}[h]{ll}
     Beneath a Steel Sky&                             [Game: sky]\\
     Simon the Sorcerer 1&                            [Game: simon1acorn/\\
     &                                                       simon1dos/\\
     &                                                       simon1talkie/\\
     &                                                       simon1win]\\
     Simon the Sorcerer 2&                            [Game: simon2dos/\\
     &                                                       simon2talkie/\\
     &                                                       simon2win\\
     &                                                       simon2mac]\\
    Flight of the Amazon Queen&                    [Game: queen]\\
    Broken Sword I&                                [Game: sword1]\\
    Broken Sword II&                               [Game: sword2]\\
  \end{tabular}

The following games should be completable, but have some critical problems that
prevent them from being fully supported at this time. Please do not file bug
reports about them.

  \begin{tabular}[h]{ll}
	Putt-Putt Joins the Parade& [puttputt]\\
  \end{tabular}

  The following games should load, but are not yet fully playable. Play these at your own risk, and please do not file bug reports about them. If you want
the latest updates on game compatibility, visit our web site and view the
compatibility chart.

\begin{tabular}{ll}
  Putt-Putt Goes To The Moon&                    [Game: puttmoon]\\
  Putt-Putt's Fun Pack&                          [Game: funpack]\\
  Fatty Bear's Birthday Surprise&                [Game: fbear]\\
  Fatty Bear's Fun Pack&                         [Game: fbpack]\\
\end{tabular}

  The following games are SCUMM engine, but NOT supported by ScummVM (yet).
  \begin{itemize}
  \item Most other Humongous Entertainment titles
  \end{itemize}
%
Please be aware that the engine may contain bugs and unimplemented features
that sometimes make it impossible to finish the game. Save often, and please
file a bug report (instructions on submitting bug reports are below) if you
encounter such a bug in a 'supported' game.
\end{itemize}
%% next section
\input {03_01.tex}
%% next section
\input {03_02.tex}
%% next section
\input {03_03.tex}
%% next section
\input {03_04.tex}


