
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "readme"
%%% End: 

\subsection{Known Problems in ScummVM 0.5.7-cvs}

This release has the following known problems. There is no need to report them,
although patches to fix them are welcome. If you discover a bug that is not
listed here, nor in the compatibility table on the web site, please see
the section on Reporting Bugs.

Indiana Jones \& the Last Crusade (EGA):
  \begin{itemize}
  \item In some rooms Indy may be able to walk to odd places
  \end{itemize}
Indiana Jones \& the Last Crusade (256):
  \begin{itemize}
  \item In some rooms Indy may be able to walk to odd places
  \end{itemize}
FM Towns versions:
  \begin{itemize}
  \item Kanji versions require the FM Towns Font ROM
  \item All the FM Towns versions of games are extremely rare,
                  And as the ScummVM team does not encourage piracy in any
                  way, we don't know where to buy or download a copy of these
                  games. Petition LucasArts to re-release them :)
  \end{itemize}
Loom (EGA):
  \begin{itemize}
  \item MIDI support requires the Roland update from LucasArts
  \end{itemize}
Monkey Island 1 (EGA):
  \begin{itemize}
  \item MIDI support requires the Roland update from LucasArts
  \end{itemize}
Sam and Max:
  \begin{itemize}
  \item Highway subgame does not behave correctly.
  \item Music is broken under Dreamcast, causing game freezes
  \end{itemize}
Beneath a Steel Sky:
  \begin{itemize}
  \item Floppy demo does not work at all
  \item Amiga versions aren't supported and probably never will be
  \item Not a bug: CD version is missing speech for some dialog
  \item ScummVM 0.5.0 contained a bug in the savegame system.
                  If you experience problems using an old savegame, it may be
                  corrupt, and you will need to start a new game using this
                  version.
  \end{itemize}
Simon the Sorcerer 2:
  \begin{itemize}
  \item Only default language (English) in data files is supported in simon2mac
  \item F10 key animation in simon2mac is different compared to
        original game
  \end{itemize}
Curse of Monkey Island:
  \begin{itemize}
  \item The "Pirate Song" scene does not play correctly 
  \item Some minor graphical glitches remain
  \end{itemize}
All CD games:
  \begin{itemize}
  \item If you are experiencing random crashes, and your game
                 plays music from CD, you have encountered a Windows bug.
                 Try copying the data files from CD to your hard disk, and
                 running them from there.
  \end{itemize}