
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "readme.tex"
%%% End: 


\subsection{Known Problems}

This release has the following known problems. There is no need to report them,
although patches to fix them are welcome. If you discover a bug that is not
listed here, nor in the compatibility list on the web site, please see
the section on reporting bugs. \ref{sect-reporting-bugs}.

CD Audio Games:
  \begin{itemize}
  \item When playing games that use CD Audio (FM-TOWNS games, Loom CD, etc)
            users of Microsoft Windows 2000/XP may experience random crashes.
            This is due to a long-standing Windows bug, resulting in corrupt
            game files being read from the CD. Please copy the game data to
            your harddrive to avoid this.
  \end{itemize}
FM-TOWNS Versions:
  \begin{itemize}
  \item The Kanji versions require the FM-TOWNS Font ROM
  \item ScummVM will crash randomly when using the FM-TOWNS Font ROM for
            the Kanji versions of the following games:
            The Secret of Monkey Island, Monkey Island 2: LeChuck's Revenge
            and Indiana Jones and the Fate of Atlantis
  \end{itemize}
Loom (EGA):
The Secret of Monkey Island (EGA):
  \begin{itemize}
  \item MIDI support requires the Roland update from LucasArts
  \end{itemize}
Beneath a Steel Sky:
  \begin{itemize}
  \item Amiga versions aren't supported
  \item Floppy demos aren't supported
  \item Not a bug: CD version is missing speech for some dialogs, this is
            normal.
  \end{itemize}
Broken Sword 1:
  \begin{itemize}
  \item Macintosh version isn't supported
  \item PlayStation 1 version isn't supported
  \end{itemize}
Broken Sword 2:
  \begin{itemize}
  \item PlayStation 1 version isn't supported
  \end{itemize}
Flight of the Amazon Queen:
  \begin{itemize}
  \item Amiga versions aren't supported
  \end{itemize}
Inherit the Earth:
  \begin{itemize}
  \item Amiga CD version isn't supported
  \end{itemize}
Simon the Sorcerer 1:
  \begin{itemize}
  \item Amiga versions aren't supported
  \item Subtitles aren't available in the English and German CD versions
            as they are missing the majority of subtitles.
  \end{itemize}
Simon the Sorcerer 2:
  \begin{itemize}
  \item Combined speech and subtitles will often cause speech to be
            cut off early, this is a limitation of the original game.
  \item Only default language (English) of data files is supported
            in Amiga and Macintosh versions.
  \end{itemize}
The Feeble Files
  \begin{itemize}
  \item Subtitles are often incomplete, they were always disabled in the
            original game.
  \end{itemize}
Humongous Entertainment Games
  \begin{itemize}
  \item No support for printing images
  \end{itemize}
