
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "readme.tex"
%%% End: 


\subsection {Broken Sword notes}

Broken Sword 1 and 2 both come with in-game cutscenes compressed using
RAD Game Tools legacy Smacker(tm) format. As RAD is unwilling to open
the older legacy versions of this format to us, and have requested we not
reverse engineer it, Revolution Software has kindly allowed us to provide
re-encoded Broken Sword cutscenes for download on our website:

  \url{http://www.scummvm.org/downloads.php}

These cutscenes are provided in MPEG2 format with OGG Vorbis audio.
Viewing these cutscenes thus requires a version of ScummVM compiled
with both libmpeg2 (preferably 0.4.0 or greater) and libVorbis support.

The cutscenes should be placed in the main game data directory. Note that
currently this requires either copying the game to hard disk or reburning
customised versions of the game CDs.

The instructions for the Broken Sword games are for the Sold-Out Software
versions, which are the ones you are probably most likely to find in stores
now.


\subsubsection{Broken Sword 1}

For this game, you'll need all of the files from the clusters directories on
both CDs. You will also need the speech.clu files from the speech directories,
but since they are not identical you'll need to rename them speech1.clu and
speech2.clu for CD 1 and 2 respectively.

In addition, you will need a music subdirectory with all of the files from the
music subdirectories on both CDs. Some of these files appear on both CDs, but
in these cases they are either identical or, in one case, so nearly identical
that it makes little difference.

ScummVM does not support the original cutscene files, so there is no need to
copy them.


\subsubsection{Broken Sword 2}

For this game, you'll need all of the files from the clusters directories on
both CDs. (Actually, a few of them may not be strictly necessary, but the ones
that I'm uncertain about are all fairly small.) You will need to rename the
speech.clu and music.clu files speech1.clu, speech2.clu, music1.clu and
music2.clu so that ScummVM can tell which ones are from CD 1 and which ones are
from CD 2. Any other files that appear in both cluster directories are
identical. Use whichever you like.

In addition, you will need the cd.bin, cd.inf and startup.inf files from the
sword2 directory on CD 1.

ScummVM does not support the original cutscene files, so there is no need to
copy them.
