\section{Supported Platforms}

ScummVM has been ported to run on many platforms and operating systems.
Links to these ports can be found either on the ScummVM web page or by a
Google search. Many thanks to the effort of porters. If you have a port of
ScummVM and wish to commit it into the main SVN, feel free to contact us!

Supported platforms include (but are not limited to):

\begin{tabular}{ll}
UNIX            &(Linux, Solaris, IRIX, *BSD)\\
Windows         \\
Windows Mobile  &(iPAQ and other handheld devices)\\
Mac OS X        \\
AmigaOS         \\
BeOS            \\
Dreamcast       \\
PalmOS          \\
Playstation 2   \\
Playstation Portable\\
RISC OS         \\
Symbian         \\
\end{tabular}

The Dreamcast port does not support The Curse of Monkey Island, nor The Dig.
The PalmOS port does not support The Curse of Monkey Island, Beneath a Steel
Sky, nor either Simon the Sorcerer 1 or 2. The Dig will only work on some
Palm devices (those with a large dynamic heap).

In the Macintosh port, the right mouse button is emulated via Cmd-Click (that
is, you click the mouse button while holding the Command/Apple/Propeller key).

For the following platforms, custom backends were supported at one point
but currently are not being maintained (usually due to lack of a qualified
maintainer). In some cases (e.g. Linux), the standard SDL support works
instead.

\begin{tabular}{ll}
Linux           &(includes iPAQs running Linux)\\
MorphOS\\
GP32   \\
\end{tabular}

We have reports about unofficial ports to the following platforms. Please
note that these are not made by us, so we neither endorse nor support them.
Use at your own risk!

\begin{tabular}{ll}
Nintendo DS\\
Xbox       \\
\end{tabular}


%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "readme.tex"
%%% End: 
