
\subsection{Multi-CD Games}
In general, ScummVM does not deal very well with multi-CD games. This
is because ScummVM assumes everything about a game can be found in one
directory. Even if ScummVM does make some provisions for asking the
user to change CD, the original games usually install a small number
of files to hard disk. Unless these files can be found on all the CDs,
ScummVM will be in trouble.

Fortunately, ScummVM has no problems running the games entirely from
hard disk, if you create a directory with the correct combination of
files. Usually, when a file appears on more than one CD you can pick
either of them.

These instructions are written for the PC versions (which in some case
is the only version) of the games. Windows and DOS use
case-insensitive file systems, so if one CD has a file called
MONKEY.DAT and another has a file called monkey.dat, they are the same
files. These instructions give file names in all lower-case names,
even if that's not always how they appear on the CDs. In fact, on
case-sensitive file systems you will have to make sure that all
filenames use either all upper- or all lower-case letters for ScummVM
to be able to find the files.

The instructions for the Broken Sword games are for the Sold-Out
Software versions, which are the ones you are probably most likely to
find in stores now.


\subsubsection{The Curse of Monkey Island}
For this game, you'll need the comi.la0, comi.la1 and comi.la2 files.
The comi.la0 file can be found on either CD, but since they are
identical it doesn't matter which one of them you use.

In addition, you'll need a resource subdirectory with all of the files
from the resource subdirectories on both CDs. Some of the files appear
on both CDs, but again they're identical.

\subsubsection{Broken Sword 1}
For this game, you'll need all of the files from the clusters
directories on both CDs. You will also need the speech.clu files from
the speech directories, but since they are not identical you'll need
to rename them speech1.clu and speech2.clu for CD 1 and 2
respectively.

In addition, you will need a music subdirectory with all of the files
from the music subdirectories on both CDs. Some of these files appear
on both CDs, but in these cases they are either identical or, in one
case, so nearly identical that it makes little difference.

ScummVM does not support the original cutscene files, so there is no
need to copy them.

\subsubsection{Broken Sword 2}

For this game, you'll need all of the files from the clusters
directories on both CDs. (Actually, a few of them may not be strictly
necessary, but the ones that I'm uncertain about are all fairly
small.) You will need to rename the speech.clu and music.clu files
speech1.clu, speech2.clu, music1.clu and music2.clu so that ScummVM
can tell which ones are from CD 1 and which ones are from CD 2. Any
other files that appear in both cluster directories are identical. Use
whichever you like.

In addition, you will need the cd.bin, cd.inf and startup.inf files
from the sword2 directory on CD 1.

ScummVM does not support the original cutscene files, so there is no
need to copy them.
